Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-10 doc/PRF2022/PRF_main.tex
new figs
Results and SM updated

%% ****** Start of file apstemplate.tex ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4.2 distribution.
%%   Version 4.2a of REVTeX, January, 2015
%%
%%
%%   Copyright (c) 2015 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.2
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showkeys' option to make keywords appear
%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-1}

@@

%\usepackage{showkeys}
\usepackage{todonotes}
\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{tabularx}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\DDD}{\boldsymbol{\mathcal{D}}}
\newcommand{\SSS}{\mathcal{S}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\ee}{\mathbf{e}}
\newcommand{\ff}{\mathbf{f}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\zz}{\mathbf{z}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\renewcommand{\tt}{\mathbf{t}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\jump}[1]{[\![ #1 ]\!]}

@@

@@

\section{Tunable hydrophobicity}
The parameters are modeled after those for
phospholipid in water~\cite{Boal}.
We use $\mu = 1$~mPa~s for the viscosity of water
at room temperature. Pure lipid components give a range of interfacial
tensions $0.7$--$5.3$~pN~nm$^{-1}$~\cite{KUZMIN2005, Petelska2012,
  Jackson2016, GarciaSaez}.
we use $\gamma=4.1$~pN~nm$^{-1}$ since
this value gave good agreement with elastic moduli of lipid bilayers~\cite{Fu20,Fu2022_JFM}.
The particle radius $c = 1.25$~nm represents one half 
of phospholipid length~\cite{Boal}, and the screening length $\rho = 5$~nm
derives from experimental force-distance measurements of hydrophobic
attraction~\cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}. 
A repulsion modulus $M = 2$~pN and 
distance $\rho_0 = 0.5$~nm gives an interparticle distance around one
particle radius, ensuring the accuracy of the boundary integral
representations~\eqref{eq:SL_BIE} and~\eqref{eq:velocity} without 
overly aggressive mesh refinement. The characteristic time
and length are $1$~ns and  $1$~nm respectively.

@@

\begin{figure}
  \begin{center}
   \includegraphics[width=1.0\textwidth]{Figures/Figure3.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    Panels (a)--(c) are a snapshot at $t=0.5\ \upmu$s of the
    multiple-component bilayer with shear rate $\dot \gamma = \{0.05,
    0.075, 0.1\}$. The initial configuration is shown in inset of panel
    (a). The streamlines are plotted in the background. Panel (d) shows
    the free energies, panel (e) shows the orientational parameter
    $\tilde{S}_2$, and panel (f) shows positional parameter E.}
\end{figure}

\section{Results}
\label{sec:results}
In this section, we subject the JP structures to various
background flows. The purpose is to understand how the self-assemblies
respond to external forcing. We then compare effective
properties of materials comprised of JPs as a function of
their amphiphilic properties.
%%%

\subsection{Bilayer configurations (BC (i)) in a linear shear flow}
To begin, we place the bilayer structure (with BC (i)) from the inset of
Figure~\ref{fig:relax}(b) in a linear shear flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma \text{ ns }^{-1} ({\bf e}_y \cdot \mathbf{x}) {\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the dimensionless shear rate, and ${\ee}_x$ and
${\ee}_y$ are horizontal and vertical unit vectors, respectively. The
initial bilayer structure consists of a small self-enclosing bilayer
(vesicle) and several pieces of bilayers.
Figure~\ref{fig:BC1_shear}(a)--(c) shows a snapshot at $t = 0.5$
$\upmu$s of the bilayer for different shear rates $\dot\gamma=
0.05,0.075,0.01$. The dynamics of the bilayer can be found in
Supplementary Movie S2, which shows
that the initial pieces of bilayers
merge and form a worm-like shape under a linear shear flow. At a low
shear rate, the bilayer constantly goes through rotation and extensional
deformation with the whole bilayer remaining intact
(Figure~\ref{fig:BC1_shear}(a)). As the shear rate increases to a
moderate value (Figure~\ref{fig:BC1_shear}(b)), the bilayer is observed
to shed a small piece of bilayer, similar to the asymmetric breakup of a
viscous drop in confinement \cite{DuFuZhuMaLi2016_AICHEJ}.
%\todo[inline]{missing citation}. 
In Figure~\ref{fig:BC1_shear}(c) the high shear rate gives rise to two
separate, nearly equal bilayers, similar to the symmetric drop breakup
under a linear shear flow \cite{Stone1994_ARFM}. For the dynamic evolution, see
Supplementary Movie S4.

%\todo[inline]{missing citation}.
%%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
%  \end{center}
%  \vspace{-20pt}  
%  \caption{\label{fig:BC1_TG} Multiple component bilayers in a Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \mu$s. The pre-relaxed initial configuration is shown in inset of panel (a). 
% The streamlines are plotted in the background. 
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%  }
%\end{figure}

We observe that the order parameter $\tilde S_2$ in
Figure~\ref{fig:BC1_shear}(e) is on average increasing. In the initial
configuration, the structure has three or four pieces of bilayer.
%
Under the shear flow, the shedding and merging of bilayers results in an
overall decrease in distinct bilayer structures. Similarly, the free
energies are slightly decreasing (Figure~\ref{fig:BC1_shear}(d)), with
the overall changes occurring in the range of a few $\mathrm{k_BT}$/nm.
This suggests that the shear flow changes the energy landscape to move
the local equilibrium obtained from a random initial condition to an
alternate local equilibrium with less free energy and greater
orientational order  (Supplementary Movie S2).  Note that the free energy $F$ in
Figure~\ref{fig:BC1_shear}(d) has the unit of force ($\mathrm{k_BT}$/nm $\approx$ 4.114 pN)
because our system
is two dimensional.
%
%\begin{figure}
%  \begin{center}
%    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
%  \end{center}
%\caption{\label{fig:ves_TG} Single vesicle in a TG flow. Panels (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \mu$s where the pre-relaxed initial configuration is shown in inset of panel (a). The streamlines are plotted in the background.
%Panel (d) plots the free energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel (f) shows positional parameter E.
%}
%\end{figure}
%
Finally, the strain parameter diverges in the large shear rate cases
(Figure~\ref{fig:BC1_shear}(f))
because the various pieces of bilayer eventually completely separate and move away from one another
under the shear flow.

%%%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure4.pdf}
  \end{center}
  \caption{
    \label{fig:Ves_shear}
A single vesicle in a shear flow. Panels (a)--(c) are snapshots for
  $\dot \gamma = \{0.05, 0.0655, 0.075\}$ at $t=0.16\ \upmu$s where the
  pre-relaxed initial configuration is shown in inset of panel (a). The
  streamlines are plotted in the background. Panel (d) shows the free
  energies; panel (e) shows orientational parameter $\tilde{S}_2$; panel
  (f) shows positional parameter E.}
\end{figure}
\citet{Fu2022_JFM} studied the hydrodynamics of a JP vesicle under a
linear shear flow. Focusing on drawing analogies to hydrodynamics of a
vesicle in continuum modeling (such as
tank-treading~\cite{keller_skalak_1982,Finken08,Shaqfeh11}, bilayer
slip~\cite{sch-vla-mik2010,denOtter2007,Zgorski2019}, and
permeability~\cite{chabanon2017, qua-gan-you2021}), our previous work
demonstrated the existence of a critical shear rate above which the JP vesicle
ruptures~\cite{grandmaison_brancherie_salsac_2021,D2SM00179A}. Based on
the these early results, we reinitialized the BC (i) configuration in
the form of a single, circular vesicle (rather than several bilayer
components) and illustrate how the three measures of structural
deformation correlate to the dynamics of a JP vesicle.

At shear rates $\dot\gamma=0.05, 0.066, 0.075$, the vesicle undergoes
familiar hydrodynamics, such as elongation along the extensional axis
and tank-treading motion, as shown in
Figure~\ref{fig:Ves_shear}(a)--(c)
and Supplementary Movie S2.
%
The circular shape is also a local equilibrium, with somewhat less
energy than the disordered state c.f., Figure~\ref{fig:BC1_shear}(d) and
Figure~\ref{fig:Ves_shear}(d). But unlike the dynamics of bilayers in
Figure~\ref{fig:BC1_shear}, the energies of the JP vesicle in
Figure~\ref{fig:Ves_shear}(d) jump from the baseline value 30
$\mathrm{k_BT}$/nm to about 32 $\mathrm{k_BT}$/nm, signaling the rupture
of the vesicle into disconnected bilayers (see
Figure~\ref{fig:Ves_shear}(d), long and short dashed curves).  After the
rupture, each piece circles around the vorticity at the center without
reconnection while the energies fluctuate slightly around a constant.

For the lowest shear rate case, the vesicle has nearly constant
orientational order $\tilde S_2 = 1$ (see Figure~\ref{fig:Ves_shear}(e),
solid curve). After the JP vesicle ruptures with $\dot\gamma= 0.066$ and
$\dot \gamma= 0.075$, we observe a greater variation in the order
parameter $\tilde{S}_2$ with a baseline value around $0.7$ (see
Figure~\ref{fig:Ves_shear}(e), dashed curves). The oscillations occur
due to the orbit of the two bilayer components, and $\tilde{S}_2$
increases to about $0.9$ when the components slide past one another and
are nearly parallel.
%
As in the previous case, peaks in the strain parameter $E$ correlate
well with changes in structural topology in the bilayer dynamics (dashed
curves in Figure~\ref{fig:Ves_shear}(f)).

%%%%%%%
%
\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure5.pdf}    
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BC1_TG} Bilayers with multiple domains in a
  Taylor-Green when $V_0 = \{0.1, 0.15, 0.2\}$ at $t=0.2\ \upmu$s. The
  pre-relaxed initial configuration is shown in the inset of panel (a).
  The streamlines are plotted in the background. Panel (d) shows the
  free energies; panel (e) shows the orientational parameter
  $\tilde{S}_2$; panel (f) shows the positional parameter $E$.}
\end{figure}
%
\subsection{Bilayer and vesicle configurations in a Taylor-Green flow}
Next, we subject the JP structures to a steady Taylor-Green (TG) background
flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty(\xx) = V_0\; \frac{\text{nm}}{\text{ns}}\;
\left(
-\cos\left(x/\lambda\right)
 \sin\left(y/\lambda\right)
         {\bf e}_x
         +\sin\left(x/\lambda\right)
         \cos\left(y/\lambda\right)
             {\bf e}_y\right),
\end{equation}
where $x = {\bf e}_x \cdot \xx$ and $y = {\bf e}_y \cdot \xx$
are the horizontal and vertical coordinates, respectively. 
The TG flow is a confining flow consisting of a checkerboard pattern
of cells with alternating circulation. We control the flow by the
dimensionless flow strength $V_0$ and the dimensionless cell size $l$
defining $\lambda = l$ nm. For most of the results in this subsection,
we use the parameter $l=2$.
%

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\textwidth]{Figures/Figure6.pdf}        
  \end{center}
\caption{\label{fig:ves_TG} A single vesicle in a TG flow. Panels
  (a)-(c) are snapshots for $V_0=\{0.1, 0.15, 0.2\}$ at $t=0.6\ \upmu$s
  where the pre-relaxed initial configuration is shown in inset of panel
  (a). The streamlines are plotted in the background. Panel (d) shows
  the free energies; panel (e) shows orientational parameter
  $\tilde{S}_2$; panel (f) shows positional parameter E.}
\end{figure}

There is no appreciable pattern in the deformation for the
case of bilayers with multiple pieces of bilayer in TG flow
(Supplementary Movie S3, right panel).
Figure~\ref{fig:BC1_TG}(a)--(c)
are the snapshots when $V_0=0.1,0.15,0.2$ at $t = 0.2$ $\upmu$s. At all
flow strengths, the bilayer pieces are separated and mixed by the
flow in neighboring cells. In the $V_0 = 0.2$ case, the flow breaks off
bilayers consisting of only a few particles, leading an increase in
energy (Figure~\ref{fig:BC1_TG}(d), long dashed curve). There is no
apparent structure to the change in the orientational order. There is an initial
increase in the strain parameter due to merging and rupture of bilayers, but the
strains remains bounded since the particles stay confined to the
neighbors of the central cell.

Patterns in the deformation, however, do emerge in the case of a vesicle
in TG flow (Supplementary Movie S3, left panel). For a vesicle in a Taylor-Green flow,
Figure~\ref{fig:ves_TG}(a)--(c) are configurations at $t=0.2\ \upmu$s
where $V_0=0.1,0.15,0.2$. Here, the circular vesicle takes on a steady
square shape for moderate flow rates $V_0 = 0.1$ and $V_0 = 0.15$. In
these cases, there is little change in the vesicle free energy and order
(Figure~\ref{fig:ves_TG}(d)--(f)). The vesicle disintegrates for $V_0 =
0.2$ (Supplementary Movie S5, left panel), leading to a jump in energy, drop in order, and increase in
strain, suggesting that the vesicle has a critical TG flow strength in
the interval $0.15 < V_0 <  0.2$ separating the intact and ruptured
end-states.

\begin{figure}
  \begin{center}
\includegraphics[width=1.0\textwidth]{Figures/Figure7.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:BTG_Scale} With $V_0=0.1$, panels (a)--(d) show
  the configurations with streamlines of a vesicle is in a TG flow at
  $t=1$ $\upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the
  relative enclosed area $A/A_0$ calculated from the bilayer midplane
  decreases over time. The inset shows the relative length $l/l_0$ which
  remains nearly constant with small magnitude of oscillations. The
  inset and main panel have the same horizontal axis.}
\end{figure}

The vesicle shape is also related to the cell size $l$.
Figure~\ref{fig:BTG_Scale}(a)--(d) show the deformation of a vesicle in
a TG flow for $V_0=0.1$ when $t = 1$ $\upmu$s. For the smallest cell
size $l = 1$ tested, the vesicle is somewhat octagonal and passes
through multiple cells (Figure~\ref{fig:BTG_Scale}(a)). For the largest
cell size $l = 4$, the vesicle is rhomboid and surrounds a single cell.

In all cases, the JP vesicle tank-treads in TG flow as it does
in the shear flow. The
direction of the tank-treading, however, varies with the cell size
(Figure~\ref{fig:BTG_Scale}(a)--(d), directed arcs). We attribute this
change in rotational orientation to the total rotational moment of the
cells that the vesicle passes through.

>>>>

%% ***A*** Start of file apstemplate.tex ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4.2 distribution.
%%   Version 4.2a of REVTeX, January, 2015
%%
%%
%%   Copyright (c) 2015 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.2
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showkeys' option to make keywords appear
%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-1}

@@

%\usepackage{showkeys}
\usepackage{todonotes}
\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{tabularx}
\usepackage{color,soul}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

% Bryan's Marcros
\renewcommand{\aa}{\mathbf{a}}
\newcommand{\bd}{\partial}
\newcommand{\dd}{\mathbf{d}}
\newcommand{\DD}{\mathcal{D}}
\newcommand{\DDD}{\boldsymbol{\mathcal{D}}}
\newcommand{\SSS}{\mathcal{S}}
\newcommand{\eeta}{\boldsymbol{\eta}}
\newcommand{\FF}{\mathbf{F}}
\newcommand{\GG}{\mathbf{G}}
\newcommand{\JJ}{\mathbf{J}}
\newcommand{\kk}{\mathbf{k}}
\newcommand{\nnu}{\boldsymbol{\nu}}
\newcommand{\ttau}{\boldsymbol{\tau}}
\newcommand{\ssigma}{\boldsymbol{\sigma}}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\RR}{\mathbf{R}}
\renewcommand{\SS}{\mathbf{S}}
\newcommand{\ee}{\mathbf{e}}
\newcommand{\ff}{\mathbf{f}}
\newcommand{\xx}{\mathbf{x}}
\newcommand{\zz}{\mathbf{z}}
\newcommand{\XX}{\mathbf{X}}
\newcommand{\uu}{\mathbf{u}}
\renewcommand{\vv}{\mathbf{v}}
\newcommand{\yy}{\mathbf{y}}
\renewcommand{\tt}{\mathbf{t}}
\newcommand{\pderiv}[2]{\frac{\partial #1}{\partial #2}}
\newcommand{\jump}[1]{[\![ #1 ]\!]}
\newcommand{\kbt}{\mathrm{k}_{\text{B}}\mathrm{T}}
\newcommand{\KBT}{k$_{\text{B}}$T}
\newcommand{\kb}{\kappa_{\text{B}}}
\newcommand{\ka}{\kappa_{\text{A}}}

@@

\hl{Qi Wang has a preprint "A hybrid phase field method for fluid-structure interactions in viscous fluids"}.

@@

\section{Tunable hydrophobicity}
\label{sec:tunable_hydrophobicity}
The parameters are modeled after those for
phospholipid in water~\cite{Boal}.
We use $\mu = 1$~mPa~s for the viscosity of water
at room temperature. Pure lipid components give a range of interfacial
tensions $0.7$--$5.3$~pN~nm$^{-1}$~\cite{KUZMIN2005, Petelska2012,
  Jackson2016, GarciaSaez}.
we use $\gamma=4.1$~pN~nm$^{-1}$ since
this value gave good agreement with elastic moduli of lipid bilayers~\cite{Fu20,Fu2022_JFM}.
The particle radius $c = 1.25$~nm represents one half 
of phospholipid length~\cite{Boal}, and the screening length $\rho = 5$~nm
derives from experimental force-distance measurements of hydrophobic
attraction~\cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}. 
A repulsion modulus $M = 2$~pN and 
distance $\rho_0 = 0.5$~nm gives an interparticle distance around one
particle radius, ensuring the accuracy of the boundary integral
representations~\eqref{eq:SL_BIE} and~\eqref{eq:velocity} without 
overly aggressive mesh refinement. The characteristic time
and length are $1$~ns and  $1$~nm respectively.

@@

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}asdf}
\end{figure}
We subjected the Type I, II, and III JP phases to background flows and measured 
their material response.  The background flows were a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal
and vertical directions, respectively. 
In both cases, $\dot \gamma$ is the shear rate.
To obtain a range for $\dot \gamma$, 
consider the capillary number 
\begin{equation}
\label{eq:capillary}
C_a = \frac{\mu \dot \gamma R^3}{\kappa}
\end{equation}
where $R = 10$ nm and $\kappa = 20\;\kbt$ are 
the characteristic phase sample radius 
and bending rigidity, respectively. 
That is, $\kappa$ gives the elastic stress 
for restoring the phase-sample shape.
Shear stress overcomes elastic stress   
when $C_a > 1$ and this yields 
$\dot \gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$ s.
Thus our values for $\dot \gamma$ range between 
$0$ ns$^{-1}$ corresponding to quiescent flow
up to $0.2$ ns$^{-1}$ capable of rupturing the sample. 
Such shear rates are compatible with molecular dynamics 
simulation \cite{Bradner}, those for large unilamellar vesicles (LUV),
\cite{Bernard2005ShearinducedPA} and shearing in blood capillary vessels 
 where shear rates range over 100--1000 s$^{-1}$ \cite{NEEDED}.

The shear flow replicates the motion of a fluid between two parallel, moving plates
excluding wall effects.  In TG flow, the flow pattern
consists of an array of counter rotating cells each with size 
$2\pi \lambda \times 2\pi \lambda$.  Throughout, we use $\lambda = 2$ nm
so that the JP phases occupy about nine cells.  To compare shear
on equal terms, the flow rate $\lambda \dot \gamma$  
was chosen for \eqref{eq:tg_flow} so that it has has the same
rate viscous dissipation per area as for \eqref{eq:sh_flow}.
In other words, 
$\int_{A} \frac{1}{2}\mu |\nabla \uu + \nabla \uu^T|^2 \,\dif A$ 
is the same for 
$\uu = \uu_{\infty}^{\text{sh}}$ as for 
$\uu = \uu_{\infty}^{\text{TG}}$
when integrated over a common cell $A$.

For initial data, the steady-state Type I amphiphiles phase
consisted of a number of disjoint bilayer components
(Figure \ref{fig:relax}(b)). To also have a single-component Type I phase, 
we reinitialized the data to have a ring-shaped vesicle bilayer.
This phase is distinguished from "bilayer" by "vesicle BL" in the figures.
For the same number of JP, the vesicle bilayer
has lower free  steady-state energy ($F = 24.6 \;\kbt$ nm$^{-1}$) than the 
disordered bilayer phase ($F = 24.6 \;\kbt$ nm$^{-1}$). 
Since the simulations are for two dimensions,
multiplying $F$ by a length gives the energy 
of a transversely invariant, three-dimensional 
phase.

Figure \ref{fig:s2esummary} (e)--(l) show the typical streamlines
for JP phases in background flow.  Although the plots only show
the region near the JP phases, the fluid velocity $\uu$ and 
order parameter $u$ are solved for in all of $\mathbb{R}^2$.
Moreover, $\uu$ satisfies the rigid boundary condition at 
every JP-fluid interface i.e., the particles interact with local
flow field and are not merely carried by background flow.

The simulation setup consisted of placing each of the three JP phases
in either a shear or TG background flow and then solving for the 
particle trajectories in time.  A total of $500$ steps were solved
for with $\Delta t = 2$ ns, yielding time courses for various 
$\dot \gamma$ up to $T = 1$ $\upmu$s.  We then post-processed the trajectories
to infer free energy $F$, alignment order $S_2$, and strain $E$.

\subsection{Strain and alignment}
The plots reveal highly distinct material responses from each phase.
Figure \ref{fig:s2esummary} (a) and (b) show the time-averaged
strain $\frac{1}{T}\int_0^T E \,\dif t$ over a broad
range of shear rates.  Strain $E$
measures the non-rigid-body deformation relative to the initial state
and expectedly increases with shear rate.
The greatest increase occurs with the Type I amphiphiles, 
suggesting that this phase has the lowest elastic modulus. In comparison, 
the  striated phase consisting of  Type III polar JP is
basically rigid.

Figure \ref{fig:s2esummary} (c) and (d) plot the time-averaged
alignment order $S_2$. The vesicle and striated phases possess
the greatest alignment order and, 
for the most part, $S_2$ decreases with increases in shear rate.
But there is an exception.  The Type I bilayer phase alignment
order actually increases under both shear and TG flows (solid squares).  
This suggests that 
the mixing action of background flow has the effect of moving the
disordered bilayer phase out of a local equilibrium and into a state
with greater order.
This surprising increase, 
brought about by combining previously broken bilayer 
end caps, is accompanied
by a slight decrease in free energy (Figure \ref{fig:fsummary}a, solid squares).

The sudden jumps in  Figure \ref{fig:s2esummary} (a) and (b)
and commensurate drops in panels (c) and (d) indicate
the existence of a critical shear rate $\gamma_*$.  This means that 
for $\gamma < \gamma_*$, the JP phase remains intact while
for $\gamma > \gamma_*$, the phase ruptures. 
For example, the vesicles phase has 
$\gamma_* = 0.05$ ns$^{-1}$ 
under shear flow and TG flow. However, the critical shear rate
is flow-pattern dependent because 
the striated phase has $\gamma_* = 0.14$ ns$^{-1}$ under shear flow
while $\gamma_* = 0.05$ ns$^{-1}$ under  TG flow.
Due to variable stress distribution, 
the critical shear rate in TG likely 
depends on the cell size parameter $\lambda$.
The disordered bilayer phase does not really possess a critical
shear rate because it already consists of several, disjoint components.
The jump in Figure \ref{fig:s2esummary} (a) (solid squares)
simply corresponds to disjoint components drifting apart in the shear
flow.  The Type II multilamellar phase did
not rupture for any of the shear rates considered.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{FSummary.pdf}
\end{center}
\caption{\label{fig:fsummary}}
\end{figure}

\subsection{Free energy}
Figure \ref{fig:fsummary} plots the time-averaged
relative free energy $\frac{1}{T}\int_0^T F - F_0 \,\dif t$ where $F_0$ is 
\eqref{eq:free_energy2} at $t = 0$.  The 
greatest increase occurs with the Type II 
multilamellar phase, with the other phases 
showing a moderate change in a few \KBT\;per 
nm.

Figure \ref{fig:fsummary} (c) plots free energy 
against $x = c E$ representing the mean  
inter-particle displacement;    
zero displacement corresponds
to an inter-particle distance where 
repulsion and attraction are in balance;
$c = 1.25$ nm is particle radius.
The energies in Figure \ref{fig:fsummary} (c) are essentially  
quadratic in $x$ suggesting that the interactions 
are harmonic locally around equilibrium.
The harmonic bond strength is strongest between 
polar JP, and greater by a factor of two and five than
that for asymmetric hydrophobes and amphiphiles,
respectively.  This makes sense when considering 
that the free energy of the steady-state striated
phase is also greatest (Figure \ref{fig:relax} (c), around 85 \KBT\;nm$^{-1}$).
However, the bond strength in the multilamellar 
phase comes in second, despite having least steady-state free energy
(around 15 \KBT\;nm$^{-1}$).
The data point to the fact that the binding properties 
do not merely scale with free energy, 
but also involve the details of the interface's
hydrophobicity 
which are tuned by \ref{eq:bc-type} in our model.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{RheologySummary.pdf}
\end{center}
\caption{\label{fig:rheologysummary}}
\end{figure}
\subsection{Rheology}
So far, we have considered static material properties, namely
constant strains maintained by an external force provided by   
background flow. Now we consider dynamic material properties.
Specifically, we look at the strain rate 
\begin{equation}
\label{eq:strainrate}
\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
\end{equation}
The reason for defining $\dot E$ in this was is that 
the shear flow $\uu_{\infty}^{\text{sh}}$
simulations correspond to a complex fluid within a drag plate
rheometer where the shear stress is set by $\mu \dot\gamma$  
and the observed, sample shear rate is $\dot E$. 
The definitions carry over to the TG flow case directly. 
Also, as a practical consideration,
the rotation of non-isotropic JP phases in the background 
flow leads to oscillation in the strain time courses 
making systematic fitting challenging (see 
Supplementary Material Figures \ref{fig:veshraw}--\ref{fig:sttgraw}). 
The integral in \eqref{eq:strainrate} averages out these oscillations
and gives physically meaningful values.

The shear stress--strain rate data are 
excellently fit by power laws.  
Figures \ref{fig:rheologysummary} (a), (b), and (c)
show the data for Type I, Type II and Type III JPs, respectively,
under both shear flow (squares) and TG flow (triangles).
The bilayer phases consisting of Type I JPs are basically Newtonian
with viscosity $0.014$ MPa\;ns $= 14$ mPa\;s,
about 14 times the the viscosity of water at room temperature
(Figures \ref{fig:rheologysummary}(a), dashed curve). 
The vesicle bilayer phase is slightly shear thickening
(Figures \ref{fig:rheologysummary}(a), solid curve).
The multilamellar phase consisting of Type II JPs
is somewhat shear thinning,  but its viscosity 
is larger than for Type I.  Finally, the striated
phase is strongly shear-thinning.  This 
further explains the rigid-like behavior of the 
striated phase found in the strain, shear-rate relationships from 
Figure \ref{fig:s2esummary}(a), (b) (triangles).

\begin{figure}[t]
\begin{center}
  \includegraphics[width=\textwidth]{critical_shear_and_cell_size.pdf}
\end{center}
\caption{\label{fig:PramChange}
In panel (a), relative change in $\dot \gamma_*$ is linear 
in the relative change of tension with slope $1$.
Conversely, relative change in $\dot \gamma_*$ 
has slope $-2$ with respect to relative change in tension.
Panels (b)--(e) show the tank-treading configuration 
of a vesicle bilayer the configurations with streamlines of a vesicle is in a TG flow at
$t=1$ $\upmu$s with $l= 1,2,3,4$, respectively. In panel (e), the
  relative enclosed area $A/A_0$ calculated from the bilayer midplane
  decreases over time. The inset shows the relative length $L/L_0$ which
  remains nearly constant with small magnitude of oscillations. The
  inset and main panel have the same horizontal axis.}
\end{figure}

\subsection{Discussion}
We chose the range of shear rates $\dot \gamma \in [0, 0.02]$ ns$^{-1}$
by analyzing the capillary number of the JP phases.  Within this range, 
there was a critical shear rate $\dot \gamma_*$ for the vesicle bilayer
and striated phases where shear stresses exceeded elastic stresses,
leading to rupture.  (The multilamellar phase did not rupture.)
By varying model parameters, we can perform a dimensional analysis 
on $\dot \gamma_*$.  Focusing on Type III JP in shear flow, 
$\dot \gamma_* = 0.14$ ns$^{-1}$ for the basic model parameters
(see Section \ref{sec:tunable_hydrophobicity}).  Increasing 
the tension parameters $\gamma$ and $M$ by 5\% (collectively denoted
$\Delta \gamma/\gamma$) led to a 4.29\% increase in critical shear
rate (denoted $\Delta \dot \gamma_*/\dot \gamma_*$).  This suggests
that critical shear rate scales linearly with the tension parameters.
Conversely, increasing the length parameters $c$, $\rho$, and $\rho_0$
by 5 \% (collectively denoted $\Delta c/c$) led to a -11.43 \% 
decrease in critical shear rate.  This points to an inverse-quadratic
scaling in length. Figure \ref{fig:PramChange}(a) summarizes the 
findings and suggest the scaling
\begin{equation}
\label{eq:CSR}
\mu \dot\gamma_* = K_{\text{III}} \frac{\gamma L}{c^2}.
\end{equation}
The scalar $K_{\text{III}}$ is specific to the striated phase under shear flow.
Here $L$ is the diameter of the phase sample, which scales proportionally 
with $\gamma^*$ since the striated phase tends to cleave during
rupture (see Supplementary Movie S4).
The scaling for vesicle bilayers in shear flow is different
and takes the form $\mu \dot\gamma_* = K_{\text{I}} \gamma c^2/(\rho L^2)$
and is proportional to particle size \cite{Fu2022_JFM}, versus inverse quadratic
like for Type III JPs.
